### 2015-05-24 docs/report/array_merging.tex
Benchmark link fixes
minor fix

For the \tsabuffer{} case there are two different options:
\begin{enumerate}
  \item If all steps in the chain perform the \code{map} transformation, then no changes are required.
  \item If there is at least one \code{filter} step, the elements need to be placed at the beginning of the resulting \tstarray{} in order to avoid \textif{holes}.
\end{enumerate}

@@

The benchmark presented only has one alternative that uses a method with a native implementation:
\bmcode{http://jsperf.com/typedarray-merge}{../../spikes/2.4.1/merge.js}

>>>>

For the \tsabuffer{} case there are two different options:
\begin{enumerate}
  \item If all steps in the chain perform the \code{map} transformation, then no changes are required.
  \item If there is at least one \code{filter} step, the elements need to be placed at the beginning of the resulting \tstarray{} in order to avoid \textit{holes}.
\end{enumerate}

@@

The benchmark presented only has one alternative that uses a method with a native implementation:
\bmcode{http://jsperf.com/typedarray-merge/2}{../../spikes/2.4.1/merge.js}
